ext_risk_copula

### 2019-02-20 ext_risk_copula.Rmd
rlist modified

qrng<-runif(10000,min=0,max=r_bf_ricker)
qr<-quantile(qrng,probs=c(.025,.975))

rlist<-unique(c(seq(from=range(qr)[1],to=rc_ricker,length.out = 5),c(seq(from=rc_ricker,to=range(qr)[2],length.out = 5))))

@@

qrng<-runif(10000,min=1,max=r_bf_hassell) # r must be > 1
qr<-quantile(qrng,probs=c(.025,.975))

rlist<-unique(c(seq(from=range(qr)[1],to=rc_hassell,length.out = 5),c(seq(from=rc_hassell,to=range(qr)[2],length.out = 5))))

@@

qrng<-runif(10000,min=1,max=r_bf_msmith) #r must be > 1 for +ve eqm pt.
qr<-quantile(qrng,probs=c(.025,.975))

rlist<-unique(c(seq(from=range(qr)[1],to=rc_msmith,length.out = 5),c(seq(from=rc_msmith,to=range(qr)[2],length.out = 5))))

@@

qrng<-runif(10000,min=1,max=r_bf_pennycuick) # r must be > 1
qr<-quantile(qrng,probs=c(.025,.975))

rlist<-unique(c(seq(from=range(qr)[1],to=rc_pennycuick,length.out = 5),c(seq(from=rc_pennycuick,to=range(qr)[2],length.out = 5))))

@@

qrng<-runif(10000,min=0,max=r_bf_verhulst)
qr<-quantile(qrng,probs=c(.025,.975))

rlist<-unique(c(seq(from=range(qr)[1],to=rc_verhulst,length.out = 5),c(seq(from=rc_verhulst,to=range(qr)[2],length.out = 5))))

@@

qrng<-runif(10000,min=0,max=r_bf_abrewer)
qr<-quantile(qrng,probs=c(.025,.975))

rlist<-unique(c(seq(from=range(qr)[1],to=rc_abrewer,length.out = 5),c(seq(from=rc_abrewer,to=range(qr)[2],length.out = 5))))

>>>>

rng1<-runif(10000,min=0,max=r_bf_ricker)
qr1<-quantile(rng1,probs=c(.025,.975))
q1<-abs(unname(qr1[1])-rc_ricker)
q2<-abs(unname(qr1[2])-rc_ricker)
qs<-c(q1,q2)
iqmin<-which.min(qs)
iqmax<-which.max(qs)

rlist<-seq(from=range(qr1)[iqmin],to=range(qr1)[iqmax], by = qs[iqmin]/4)

xx<-diff(rlist)
vxx<-var(xx)

if(vxx>1e-10){
  warning("Not equal spacing in rlist : Ricker model !!!",immediate.=T,call.=T)
}

@@

rng1<-runif(10000,min=1,max=r_bf_hassell) # r must be > 1
qr1<-quantile(rng1,probs=c(.025,.975))
q1<-abs(unname(qr1[1])-rc_hassell)
q2<-abs(unname(qr1[2])-rc_hassell)
qs<-c(q1,q2)
iqmin<-which.min(qs)
iqmax<-which.max(qs)

rlist<-seq(from=range(qr1)[iqmin],to=range(qr1)[iqmax], by = qs[iqmin]/4)

xx<-diff(rlist)
vxx<-var(xx)

if(vxx>1e-10){
  warning("Not equal spacing in rlist : Hassell model !!!",immediate.=T,call.=T)
}

@@

rng1<-runif(10000,min=1,max=r_bf_msmith) #r must be > 1 for +ve eqm pt.
qr1<-quantile(rng1,probs=c(.025,.975))
q1<-abs(unname(qr1[1])-rc_msmith)
q2<-abs(unname(qr1[2])-rc_msmith)
qs<-c(q1,q2)
iqmin<-which.min(qs)
iqmax<-which.max(qs)

rlist<-seq(from=range(qr1)[iqmin],to=range(qr1)[iqmax], by = qs[iqmin]/4)

xx<-diff(rlist)
vxx<-var(xx)

if(vxx>1e-10){
  warning("Not equal spacing in rlist : Maynard-smith model !!!",immediate.=T,call.=T)
}

@@

rng1<-runif(10000,min=1,max=r_bf_pennycuick) #r must be > 1 for +ve eqm pt.
qr1<-quantile(rng1,probs=c(.025,.975))
q1<-abs(unname(qr1[1])-rc_pennycuick)
q2<-abs(unname(qr1[2])-rc_pennycuick)
qs<-c(q1,q2)
iqmin<-which.min(qs)
iqmax<-which.max(qs)

rlist<-seq(from=range(qr1)[iqmin],to=range(qr1)[iqmax], by = qs[iqmin]/4)

xx<-diff(rlist)
vxx<-var(xx)

if(vxx>1e-10){
  warning("Not equal spacing in rlist : Pennycuick model !!!",immediate.=T,call.=T)
}

@@

rng1<-runif(10000,min=0,max=r_bf_verhulst)
qr1<-quantile(rng1,probs=c(.025,.975))
q1<-abs(unname(qr1[1])-rc_verhulst)
q2<-abs(unname(qr1[2])-rc_verhulst)
qs<-c(q1,q2)
iqmin<-which.min(qs)
iqmax<-which.max(qs)

rlist<-seq(from=range(qr1)[iqmin],to=range(qr1)[iqmax], by = qs[iqmin]/4)

xx<-diff(rlist)
vxx<-var(xx)

if(vxx>1e-10){
  warning("Not equal spacing in rlist : Verhulst model !!!",immediate.=T,call.=T)
}

@@

rng1<-runif(10000,min=0,max=r_bf_abrewer)
qr1<-quantile(rng1,probs=c(.025,.975))
q1<-abs(unname(qr1[1])-rc_abrewer)
q2<-abs(unname(qr1[2])-rc_abrewer)
qs<-c(q1,q2)
iqmin<-which.min(qs)
iqmax<-which.max(qs)

rlist<-seq(from=range(qr1)[iqmin],to=range(qr1)[iqmax], by = qs[iqmin]/4)

xx<-diff(rlist)
vxx<-var(xx)

if(vxx>1e-10){
  warning("Not equal spacing in rlist : Austin-Brewer model !!!",immediate.=T,call.=T)
}
